### 2023-06-11 resilience-safe-up.tex
up

%
%		cas étudié par les deux articles sur les graphes
%
Let us choose $\Bad$ to be the set of states from which there is no infinite run. If we are in an upward compatible ordered transition system (like VASS, lossy channel systems,...), then $\Bad$ is downward-closed.
\alain{ce qui précède est faux et pas convaincant: un vass qui seulement décroit ses compteurs}

%Such a Turing machine, in combination with $M_\rightarrow$, allows computing
%$\post(x)$ whenever the latter is finite.

@@

example: in a VASS, we may choose $\Safe$ to be the set of states that are not deadlocks, i.e. from which it is always possible to fire a transition. This set of states is upward-closed and $\Safe=S-\Bad=\uparrow \Safe$.\alain{mal rédigé}

>>>>

We start with the case $\Bad=\downarrow \Bad$ and $\Safe=\uparrow \Safe$. 
It can be viewed as a generalizeation/extension of coverability, namely,
it asks whether for every element of $\Bad$ it is possible to cover an element of the basis of $\Safe$.

% Let us choose $\Bad$ to be the set of states from which there is no infinite run. If we are in an upward compatible ordered transition system (like VASS, lossy channel systems,...), then $\Bad$ is downward-closed.
% \alain{ce qui précède est faux et pas convaincant: un vass qui seulement décroit ses compteurs}

@@

As an
example: in a VASS, we may choose $\Safe$ to be the set of states that are not deadlocks, i.e. from which it is always possible to fire a transition. This set of states is upward-closed and $\Safe=S \setminus \Bad=\uparrow \Safe$.\alain{mal rédigé}

### 2023-06-11 resilience.tex
up

>>>>

In this section we introduce the concept of resilience for well structured transition systems. We show that the resilience problems are decidable
for  completion-post-effective $\omega^2$-WSTS with strong compatibility
when [...]
and for downward-compatible ideal-effective WSTS
when [...]. 
We show that resilience problems are however undecidable for WSTS with
strong compatibility in general.
